---
title       : Developing Data Products Course Project
subtitle    : Finance Calculator
author      : Robert Richter
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides

---

## Basics of the Finance calculator  

Finance calculator determines the future capital, given a starting capital, a annual interest rate and a time scale.   

###  Input parameters

- starting capital
- annual interest rate
- time of the investment

### Output

- future capital

---

## Theory
Recall all the variables

- starting capital (in Dollars) :     $\Large{C_S}$
- annual interest rate (in %)   :     $\Large{p}$ 
- time of the investment (in years)   $\Large{Y}$
- future capital (in Dollars) :       $\large{C_F}$

The future capital will be caluclated via the following formula

$$ \Large{C_F= C_S \left(1+\frac{p}{100} \right)^Y}$$

---


## Code  ui.R

```{r,echo=TRUE,results=FALSE, cache=FALSE}
shinyUI(pageWithSidebar(
        headerPanel("Finance Calculator"),        
        sidebarPanel(
                p('Enter your starting capital you want to invest, the time you want invest it as well as the average interest rate.
                    '),
                h3("Initial capital"),
                numericInput('capital', label='Dollars',0),
                h3("Time"),
                numericInput('years', label='years',0),
                h3("Interest rate per year"),
                numericInput('rate', label='%',0)
        ),
        mainPanel(
                h3("Future capital "),
                p('Given the data your future capital will be (in Dollars)'),
                verbatimTextOutput("prediction"))
))
```

---

## Code server.R

```{r, echo=TRUE, results='hide', cache=FALSE}
library(shiny)
outcome <-function(capital, years, rate) capital*(1+rate/100)^years 
shinyServer(
    function(input, output){
        output$prediction <- renderPrint({outcome(input$capital, input$years, input$rate)})
    }
                )
```

## Link to the application


Finally let us display also the link for the application


https://robrichter1979.shinyapps.io/course_project